Information Closure Theory of Consciousness

### 2019-09-28 Paper_neural_coarse_graining_of_consciousness.tex
Replace dirty talk to cquotes

        Based on the hypothesis, \ac{OurTheory} leads to five core implications: 
        \begin{description}
            \item[Implication 1.] 
            Consciousness is information. Here, "informative" refers to the resolution of uncertainty. Being in a certain conscious state rules out other possible conscious states. Therefore, every conscious percept resolves some amount of uncertainty and provides information. \\ 
            This implication is also in agreement with the "axiom" of \textit{information} in Integrated Information Theory (IIT 3.0) which claims that \myQuote{...an experience of pure darkness is what it is by differing, in its particular way, from an immense number of other possible experiences...} \citep[p.2]{oizumi2014phenomenology}.

@@

            \textbf{The concept of "information"}: In IIT, information refers to "integrated information":\\ \say{Information that is specified by a system that is irreducible to that specified by its parts.}~\citep{tononi2016integrated} In \ac{OurTheory}, information refers to "self-information", i.e. information about the states of conscious experience and the physical states of a process. Therefore, IIT focuses more on the relationships between consciousness and causal interactions among elements within a system, whereas \ac{OurTheory} focuses more on the informational relationships between conscious experience and being in a certain state of a process.

>>>>

        Based on the hypothesis, \ac{OurTheory} leads to five core implications: 
        \begin{description}
            \item[Implication 1.] 
            Consciousness is information. Here, "informative" refers to the resolution of uncertainty. Being in a certain conscious state rules out other possible conscious states. Therefore, every conscious percept resolves some amount of uncertainty and provides information. \\ 
            This implication is also in agreement with the "axiom" of \textit{information} in Integrated Information Theory (IIT 3.0) which claims that \textquote[{\citealp[P.~2]{oizumi2014phenomenology}}]{...an experience of pure darkness is what it is by differing, in its particular way, from an immense number of other possible experiences...}

@@

            \textbf{The concept of "information"}: In IIT, information refers to "integrated information":\\ \textquote[\citealt{tononi2016integrated}]{Information that is specified by a system that is irreducible to that specified by its parts.} In \ac{OurTheory}, information refers to "self-information", i.e. information about the states of conscious experience and the physical states of a process. Therefore, IIT focuses more on the relationships between consciousness and causal interactions among elements within a system, whereas \ac{OurTheory} focuses more on the informational relationships between conscious experience and being in a certain state of a process.
